Data Specialization for a Staged Lambda Calculus

### 2015-01-30 paper/paper.tex
changes to figures
switch to icfp formatting
edits all over (syntax) and masking section
changed staged quickselect code

\documentclass[pldi,preprint]{sigplanconf}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
%\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
%\usepackage[utf8x]{inputenc}
%\PrerenderUnicode{λ}
\usepackage{verbatim}

@@

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {$}{{$\fut$}}1}

@@

\section{Intro}
(placeholder in order to keep section numbers stable)

>>>>

\documentclass[preprint]{sigplanconf}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\PrerenderUnicode{λ}
\usepackage{verbatim}

@@

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {atsign}{{@}}1
                 {^}{{$\curr$}}1
                 {$}{{$\fut$}}1}

@@

\section{Intro}

(placeholder in order to keep section numbers stable)
